\fancyhead{}

\vspace*{1cm}
\begin{center}
    \textbf{\huge{General Conclusion}}
\end{center}
\vspace{1cm}

\begin{doublespace}
This internship at Renault Digital Morocco provided valuable hands-on experience in enterprise software development within the cybersecurity domain. Working on the Key Management System allowed for practical application of modern Java technologies and agile development methodologies in a real-world industrial context.

The project highlighted the importance of understanding business requirements beyond technical specifications. Developing a notification system required careful consideration of user workflows, organizational roles, and operational constraints—demonstrating that effective software solutions must balance technical capabilities with human factors.

From a technical perspective, the integration of multiple technologies—Spring Boot, message queuing, WebSocket communication, and database design—reinforced the complexity of enterprise application development. The experience emphasized the value of modular architecture and the challenges of maintaining system reliability in production environments.

This internship strengthened both technical skills and professional competencies, particularly in requirements analysis, system design, and collaborative development. The exposure to Renault's engineering practices and quality standards provides a solid foundation for future career development in enterprise software engineering.

The project serves as a practical example of how targeted automation can address specific operational needs while contributing to broader organizational objectives in security and compliance.
\end{doublespace}